Universal Anonymous Signatures

### 2022-06-18 prism-backend/research/gsac/conclusion-paper.tex
Beginning refurbishment of the paper.

In this work, we have described how a direct combination of the group signatures
(GS) and anonymous credentials (AC) research lines results in a scheme that can
bring benefit to real world use cases. Going further, we generalized such simple
combination into Universal Anonymous Signatures, or \UAS. Our model for \UAS
covers straight away a large subset of GS and AC variants, while still giving
system designers the flexibility to decide on the specific tradeoff between
privacy, utility, accountability and computational overhead that fits their
setting best. More concretely, our model for \UAS supports arbitrary issuance
policies, signature evaluation functions, and opening functions, without losing
definitional meaning. We also gave a generic construction from well known
building blocks, and prove that it meets our security model.

Even though the generalization effort we do is significant, there are still
ways to go further.
%
For instance, we do not hide the issuer(s) of the
credential(s) employed to produce a signature (resp., request a new credential).
Thus, we can only ensure privacy among signatures (resp., credential requests)
that involve credentials issued by the same issuer set. While hiding the issuers
of the involved credentials is certainly possible (we show how to do it at
signing time, in order to build ring signatures), we argue that it may be
desirable to leave it as is, at least, initially. The reason being that issuers
are still what conveys trust to a system where credentials contain attributes
attested by these issuers. Indeed, if it is already hard for verifiers to decide
whether or not to trust a non-anonymous issuer, one can imagine that it would be
even harder to decide whether or not to trust an anonymous one. This question
is core to the domain of trust registries, for instance.
%
A second desirable improvement, perhaps clearer from a technical point of view,
is to extend our model to support non-trivial utility and accountability across
multiple signatures from the same signer. More concretely, let our \feval and
\finsp functions (and perhaps also \fissue?) operate on multiple signatures by
the same \usk. That can lead to an extended \UAS scheme which would support
advanced use cases such as rate limiting (or $k$-TAA \cite{asm06}); or might
be even privately training an AI model based on one's authenticated
past activity, and prove that the model has been trained honestly.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:

>>>>

[1 page max]

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas-paper"
%%% End:

### 2022-06-18 prism-backend/research/gsac/preliminaries-paper.tex
Beginning refurbishment of the paper.

\subsection{Related Work}
\label{ssec:related}

\paragraph{Group Signatures and Anonymous Credentials.} %
\todo{Brief summary of GS and AC here. Maybe split them in different
  paragraphs.}

\paragraph{Attribute-Based Group Signatures.} %
The closest related works to our \GSAC are the series of Attribute-Based Group
Signature schemes (ABGS) published between 2007 and 2014. The initial proposals
\cite{khad07a,khad07b} defined a variant of group signatures in which membership
credentials contained attributes. Yet, there are some
crucial differences that make ABGS too rigid for practice. Ignoring that the
first works \cite{khad07a,khad07b} are modelled as static group signatures
(i.e., they do not allow dynamic joins of new members), each group has a static
``attribute access tree'' associated to it. This tree defines what combinations
of attributes make a signature valid. For instance, an example given in
\cite{khad07b} requires group signatures to originate from an employee who is
``a member of the IT department, and either at least a junior manager from the
cryptography group, or a senior manager from the biometrics team''. If,
eventually, a different attribute access tree is needed, a new group needs to
be created. Additionally, only revocation is considered in \cite{khad07b},
which is a subset of the accountability flavours that can be reached through
the open function of conventional GS schemes. These schemes also lack formalism
in their definitions. For instance, correctness does not cover correctness of
revocation, and the anonymity definition does not seem to consider trivial wins
by the adversary in which the adversary can revoke one of the two challenge
users.
%
\cite{emo09} follows the attribute access tree aproach, but generalizes it so
that attributes can be removed from the access tree, or the required conditions
can be modified -- e.g., in \cite{emo09}, we could remove the ``or a senior
manager from the biometrics team'' condition in the previous example. It also
allows dynamic joins, and models open rather than just revocation. However,
it does not
allow adding new attributes; in that case, a new group has to be created. It
also deviates from the conventional group signatures model, by introducing a
\emph{collision-resistance} property that prevents different users from
combining their membership credentials. While this is just a modelling choice
with no impact in the actual functionality, it seems that this could be
integrated within the existing traceability property, leading to a cleaner
model. \todo{How does removing attributes or changing the access rules affect
  anonymity? Is this considered?}
%
Finally, and as far as we know, \cite{aa14} is the last work in this ABGS line.
They support dynamic joins, open and verifier-local revocation (hence, their
variant is named VLR-ABGS). Furthermore, they include backwards unlinkability,
meaning that a compromise of a user key at epoch $t$ does not affect anonymity
of signatures on previous epochs by that same user. This scheme is still based
on attribute access trees -- concretely, those in \cite{emo09}, and thus
inherits its constraints. It also resorts to many properties, deviating from the
cleaner approaches of GS schemes. Specifically, it defines security of VLR-ABGS
by means of attribute anonymity (which is not formally defined),
backwards-unlinkability user anonymity, traceability, non-frameability,
attribute unforgeability, and collision resistance of attributes. Again, this
are just modelling choices, but it would seem that several of these properties
could be collapsed, hence leading to a cleaner model, much easier to evaluate
(e.g., traceability, attribute unforgeability and collision resistance of
attributes all seem similar).

In summary, the previous line of ABGS seems to lack the flexibility of AC
schemes in regards to what can be proven with attribute-based credentials.
Restricting to AC with selective disclosure, one can get essentially the same
functionality as with ABGS, but with flexible policies. That is, just let
the verifier specify the policy that users need to meet depending on the
situation, and only users revealing a matching subset of attributes will be
accepted. In this respect, anonymity and unforgeability of ACs are equivalent to
anonymity and traceability/unforgeability properties of ABGS. Still, an ABGS
group is tied up to one concrete policy, while a single AC scheme spans
arbitrarily many.
%
On the other hand, what ABGS (or, rather, some of its variants) adds with
respect to AC schemes is the non-frameability property of group signatures,
which opens the possibility to easily incorporate accountability notions.
%
In addition to what we have already mentioned, none of the ABGS works allows
a group member to obtain multiple credentials -- not even from the same issuer.
While obtaining multiple credentials in the setting of GS is not useful, it is
if we include attributes and realize that the same user may have multiple
attributes. This is certainly the case in multiple real life scenarios. For
instance, the same person may obtain two different degrees within the same
university; or an employee of a bank can also be a client. Both situations
require attribute credentials issued by the same entity (the university, or
the bank), none of them being a proper subset of the other, but still being
associated to the same person.

% One difference between our current approach to GSAC, and the existing ABGS
% works, is that in ABGS each group member can only get one credential. On the
% other hand, we are trying to let any group member obtain as many credentials
% as he wishes, possibly with different attributes, albeit all of them related to
% the same user key pair (if a different user key pair is employed, then this is
% considered as a different user).

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:

>>>>

[3 pages max; 1.5 prelim, 1.5 GSAC]

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas-paper"
%%% End:

### 2022-06-18 prism-backend/research/gsac/uas-paper.tex
Beginning refurbishment of the paper.

\documentclass{llncs}%[10pt]{llncs}
\pagestyle{plain}

@@

\begin{abstract}
  Much work has been done in the last 4 decades on privacy-preserving
  identities and authentication that tries to incorporate some sort of utility
  and accountability without losing (too much) privacy. Among the most relevant
  efforts we can find group signatures (GS) and anonymous credentials (AC).
  %
  AC let users obtain attestations by trusted
  issuers on certain attributes -- thus implicitly defining the concept of
  identity as ``a set of attributes'' -- and allow credential owners to prove
  claims on these attributes. While this has proven to be very
  flexible, accountability in AC schemes is quite limited; frequently restricted
  to blacklisting, if present at all.
  %
  On the other hand, GS have traditionally focused on plain authentication
  without attributes, making instead more emphasis on the accountability side.
  That is, not only allowing full
  deanonymization, but also variants such as sequential linking, user-controlled
  anonymity, or even full unlinkability.
  %
  Not surprisingly, GS and AC share very common syntax, models and frequently
  also constructions.

  We argue that, in the real world, both functionalities are essential. Taking
  advantage of their similarities, we first propose a trivial combination,
  \GSAC, showcasing the benefits even a simple combination brings. We give a
  common syntax, security model, and generic construction for \GSAC.
  %
  Next, we generalize \GSAC into our Universal Anonymous Signatures (\UAS)
  proposal by allowing arbitrary policies at issuance, signing and opening
  time, among other improvements. While generalizations along these
  lines have been explored independently in the GS and AC domains, to the best
  of our knowledge, no single scheme offers such full flexibility.
  We define a syntax, security model, and give a generic construction for a
  scheme meeting these requirements. Furthermore, we show how our model for
  \UAS is a generalization of previous well known schemes in the GS and AC
  domains.
  %
  The techniques and building blocks we leverage are well known. The challenge
  is, rather, on the definitional side. To further evidence the universality of
  \UAS, we show how more restricted schemes can be built from vanilla \UAS.
\end{abstract}

\tableofcontents

\input{introduction.tex}
\input{preliminaries.tex}
\input{sec-gsac.tex}
\input{sec-uas.tex}
%\input{benchmarks.tex}
\input{conclusion.tex}

\bibliographystyle{splncs04}
\bibliography{uas}

\appendix

\input{app-building-blocks.tex}
\input{app-gsac.tex}
\input{app-model-related.tex}

>>>>

\documentclass{llncs}
\pagestyle{plain}

@@

\begin{abstract}
  \todo{XXX}
\end{abstract}

\input{introduction-paper.tex}
\input{preliminaries-paper.tex}
\input{formal-uas.tex}
\input{relationships.tex}
\input{conclusion-paper.tex}

\bibliographystyle{splncs04}
\bibliography{uas-paper}

% \appendix

% \input{app-building-blocks.tex}
% \input{app-gsac.tex}
% \input{app-model-related.tex}
